\documentclass[10pt,a4paper]{article}

% Tight printable margins
\usepackage[a4paper,margin=1.4cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

% PDF meta
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  pdftitle={Juluri Dileep Goud - ATS Resume},
  pdfauthor={Juluri Dileep Goud}
}

\flushbottom
\pagestyle{empty}

% --- GLOBAL ALIGNMENT ---
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlength{\tabcolsep}{0pt}

% safer column types: X for flexible width, P for fixed width (p-like)
\newcolumntype{X}{>{\raggedright\arraybackslash}X}
\newcolumntype{P}[1]{>{\raggedleft\arraybackslash}p{#1}}

% --- SECTION STYLE ---
\titleformat{\section}
  [block]
  {\bfseries\normalsize}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{2pt}\titlerule]

\titlespacing{\section}{0pt}{6pt}{4pt}

% Compact item spacing (portable settings)
\setlist[itemize]{leftmargin=*, itemsep=1.5pt, topsep=2pt, parsep=0pt, partopsep=0pt, labelsep=6pt}

\newcommand{\lbl}[1]{\textbf{#1}\hspace{4pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\Large\bfseries JULURI DILEEP GOUD}\\[2pt]
  \normalsize Certificate in AI Data Analytics\\[4pt]
  \small
  \href{tel:+918179062225}{+91 81790 62225} \;|\;
  \href{mailto:dileepgoud6222@gmail.com}{dileepgoud6222@gmail.com} \;|\;
  \href{https://www.linkedin.com/in/dileep-goud/}{LinkedIn} \;|\;
  \href{https://github.com/dileep6222}{GitHub}
\end{center}

% ===== CAREER OBJECTIVE =====
\section{Career Objective}
Aspiring \textbf{AI/ML Engineer} with strong foundations in Python, Machine Learning, Deep Learning, and Data Analytics. Skilled in building ML models and deploying AI applications using TensorFlow, Scikit-learn, FastAPI, and Streamlit. Seeking to apply analytical and problem-solving abilities to create scalable AI solutions.

% ===== EDUCATION =====
\section{Educational Qualifications}
\begin{tabularx}{\textwidth}{@{} X P{3cm} @{}}
\textbf{B.Tech — CSE (IoT)} & 2021--2025 \\
Malla Reddy Engineering College, Hyderabad & \\
\\[-2pt]
\textbf{Intermediate — MPC} & 2019--2021 \\
Telangana Residential Junior College, Suryapet & \\
\\[-2pt]
\textbf{SSC} & 2019 \\
Naagarjuna Model School, Hyderabad & \\
\end{tabularx}

% ===== SKILLS =====
\section{Technical Skills}
\lbl{Programming:} Python, SQL, C (Basics) \\
\lbl{ML \& AI:} Supervised \& Unsupervised ML, Deep Learning, NLP, LLMs, Generative AI \\
\lbl{Libraries:} NumPy, Pandas, Matplotlib, Seaborn, Scikit-learn, TensorFlow \\
\lbl{Frameworks/Tools:} FastAPI, Flask, Streamlit, LangChain, Rasa, Git, Power BI \\
\lbl{Data Skills:} Data Cleaning, EDA, Feature Engineering, Visualization \\
\lbl{Notebooks:} Jupyter Notebook, Google Colab

% ===== PROJECTS =====
\section{Projects}
\textbf{Bone Tumor Identification Using X-Ray Images (Deep Learning)} \\
\begin{itemize}
  \item Developed a CNN model for X-ray tumor classification using TensorFlow/Keras.
  \item Performed data augmentation, hyperparameter tuning, and model evaluation.
  \item Deployed the model via a Streamlit interface for real-time predictions.
\end{itemize}

\textbf{Child Mortality Prediction Using Machine Learning} \\
\begin{itemize}
  \item Built ML models using Logistic Regression, Random Forest, and SVM.
  \item Conducted preprocessing, visualization, feature selection, and evaluation.
  \item Tools: Python, Pandas, NumPy, Scikit-learn, Matplotlib.
\end{itemize}

% ===== CERTIFICATIONS =====
\section{Certifications}
\begin{itemize}
  \item AI Data Analytics — Tech Mahindra SMART Academy (Dec 2025)
\end{itemize}

% ===== STRENGTHS =====
\section{Strengths}
\begin{itemize}
  \item Quick learner
  \item Strong problem-solving skills
  \item Time management
  \item Self-motivated
  \item Teamwork and collaboration
  \item Leadership qualities
\end{itemize}

% ===== LANGUAGES =====
\section{Languages} 
\begin{itemize}
  \item English
  \item Telugu
  \item Hindi
\end{itemize}

% ===== PORTFOLIO =====
\section{Portfolio}
\begin{itemize}
  \item \href{https://dileep6222.github.io/dileep.github.io/}{Dileep portfolio}
\end{itemize}

\end{document}
